### 2023-12-06 to_do.tex
to do list changes from ages ago

Code:
* compressible Boussinesq equations class and examples
* general mixed solve for the compressible Euler equations
* merge transport wrapper PR and update all examples and scripts
* fix vorticity function space
* check hydrostatic Euler is correct
* better provision of solver options?

@@

Figures:
* cubed sphere and icosahedral sphere grids
* extruded mesh?
* DOFs?
* convergence plot of SW W2 (and W3?) for a range of timestepping schemes
* snapshots of W5 (after 15 and 50 days), W6 and Galewsky
* vertical slice gravity wave final state
* vertical slice flow over orography
* dense bubble
* rising bubble

>>>>

Code:
* compressible Boussinesq equations class and examples
* general mixed solve for the compressible Euler equations
DONE* merge transport wrapper PR and update all examples and scripts
DONE?* fix vorticity function space
* check hydrostatic Euler is correct
* check SUPG is correct
* better provision of solver options?

@@

Figures:
* cubed sphere and icosahedral sphere grids
* extruded mesh?
* DOFs?
* convergence plot of SW W2 (and W3?) for a range of timestepping schemes
* snapshots of W5 (after 15 and 50 days), W6 and Galewsky [suggest: W5 and W6 at both orders; Galewsky on both icosahedral and cubed spheres]
* vertical slice gravity wave final state
* vertical slice flow over orography
* dense bubble
* something in 3D
